---
title: "repayment_eda"
author: "Lyufan Pan"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(stringr)
library(skimr)
```

```{r}
repayment <- read_csv("repayment.csv")
```

pivot longer repayment file
```{r}
rp <- repayment %>% 
  pivot_longer(cols = contains("rpy"),
               names_to = "name",
               values_to = "value") %>% 
  drop_na()
```

Missing values for each year:

2008 - 1yr,                1yr_n 
2009 - 1yr, 3yr,           1yr_n, 3yr_n
2010 - 1yr, 3yr,           1yr_n, 3yr_n
2011 - 1yr, 3yr, 5yr,      1yr_n, 3yr_n, 5yr_n
2012 - 1yr, 3yr, 5yr,      1yr_n, 3yr_n, 5yr_n
2013 - 1yr, 3yr, 5yr, 7yr, 1yr_n, 3yr_n, 5yr_n, 7yr_n
2014 - 1yr, 3yr, 5yr, 7yr, 1yr_n, 3yr_n, 5yr_n, 7yr_n
2015 -      3yr, 5yr, 7yr,        3yr_n, 5yr_n, 7yr_n
2016 -      3yr, 5yr, 7yr,               5yr_n, 7yr_n
2017 - NA


split into two version - number or rate
```{r}
rp_rt <- rp[sapply(rp$name, function(x) grepl("yr_rt", x)),]
rp_n <- rp[sapply(rp$name, function(x) grepl("yr_n", x)),]
```

## rp_rt
```{r}
# split the name into characteristic and period
split_rt <- sapply(rp_rt$name, function(x) strsplit(x, "_rpy_"))

rp_rt$characteristic <- sapply(split_rt, function(x) x[[1]])
rp_rt$period <- sapply(split_rt, function(x) x[[2]])
```

```{r}
rp_rt$characteristic[rp_rt$characteristic == "compl"] <- "completer"
rp_rt$characteristic[rp_rt$characteristic == "noncom"] <- "non_completer"
rp_rt$characteristic[rp_rt$characteristic == "lo_inc"] <- "low_income"
rp_rt$characteristic[rp_rt$characteristic == "md_inc"] <- "middle_income"
rp_rt$characteristic[rp_rt$characteristic == "hi_inc"] <- "high_income"
rp_rt$characteristic[rp_rt$characteristic == "dep"] <- "dependent"
rp_rt$characteristic[rp_rt$characteristic == "ind"] <- "independent"
rp_rt$characteristic[rp_rt$characteristic == "pell"] <- "pell_grant"
rp_rt$characteristic[rp_rt$characteristic == "nopell"] <- "non_pell_grant"
rp_rt$characteristic[rp_rt$characteristic == "firstgen"] <- "first_generation"
rp_rt$characteristic[rp_rt$characteristic == "notfirstgen"] <- "non_first_generation"

rp_rt$period[rp_rt$period == "1yr_rt"] <- "1_year"
rp_rt$period[rp_rt$period == "3yr_rt"] <- "3_year"
rp_rt$period[rp_rt$period == "5yr_rt"] <- "5_year"
rp_rt$period[rp_rt$period == "7yr_rt"] <- "7_year"
```

```{r}
rt_median <- rp_rt %>% 
  group_by(year, characteristic, period) %>% 
  summarise(median = median(value, na.rm = T))

rt_median
```

1. different counting characteristics by repayment periods
```{r}
ggplot(rt_median[rt_median$period=="3_year",], aes(x = year, y = median, color = characteristic))+
  geom_path()+
  labs(title = "Repayment rate for different student characteristics",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5))
```
For different repayment period (1/3/5/7 years), all counting characteristics indicate a decrease in repayment rate.

2. different repayment periods by counting characteristics
```{r}
rt_median2 <- rp_rt %>% 
  group_by(year, period) %>% 
  summarise(median = median(value, na.rm = T))

rt_median2

ggplot(rt_median2, aes(x = year, y = median, color = period))+
  geom_path(size = 1) +
  labs(title = "Repayment rate for different period of repayment",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5))
```
The repayment rate for different counting characteristics all follow the rule that 7-year has the highest repayment rate, while 1-year has the lowest repayment rate.

3. income level
```{r}
income <- rt_median[sapply(rt_median$characteristic, function(x) grepl("income", x)),]
income$characteristic <- factor(income$characteristic, level = c("low_income", "middle_income", "high_income"))

ggplot(income, aes(x = factor(year), y = median, fill = characteristic))+
  geom_bar(stat = "identity",  position = "dodge") +
  labs(title = "Repayment rate at different income level",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5))


# income level by repayment period
# ggplot(income, aes(x = factor(year), y = median, fill = characteristic))+
#   geom_bar(stat = "identity",  position = "dodge") +
#   facet_wrap(~period)
# 
# ggplot(income, aes(x = year, y = median, color = characteristic))+
#   geom_path(size = 1) +
#   facet_wrap(~period)
```

4. gender
```{r}
gender <- rt_median[sapply(rt_median$characteristic, function(x) grepl("male", x)),]

ggplot(gender, aes(x = factor(year), y = median, fill = characteristic))+
  geom_bar(stat = "identity",  position = "dodge")

ggplot(gender, aes(x = year, y = median, color = characteristic))+
  geom_point(alpha = 0.7) +
  geom_path(size = 1) +
  facet_grid(.~period)

ggplot(gender, aes(x = year, y = median))+
  geom_bar(aes(fill = characteristic),stat = "identity",  position = "dodge", alpha = 0.7) +
  geom_path(aes(color = characteristic), size = 1)+
  facet_wrap(~period)
```

5. first-generation
```{r}
generation <- rt_median[sapply(rt_median$characteristic, function(x) grepl("generation", x)),]
# 
# ggplot(generation, aes(x = factor(year), y = median, fill = characteristic))+
#   geom_bar(stat = "identity",  position = "dodge")

ggplot(generation, aes(x = year, y = median, color = characteristic))+
  geom_point(alpha = 0.7) +
  geom_path(size = 1) +
  facet_wrap(.~period) +
  labs(title = "Repayment rate by student generation",
       subtitle = "first-generation VS non-first-generation",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

# ggplot(generation, aes(x = year, y = median))+
#   geom_bar(aes(fill = characteristic),stat = "identity",  position = "dodge", alpha = 0.7) +
#   geom_path(aes(color = characteristic), size = 1)+
#   facet_wrap(~period)
```

6. completer
```{r}
completer <- rt_median[sapply(rt_median$characteristic, function(x) grepl("completer", x)),]
ggplot(completer, aes(x = factor(year), y = median, fill = characteristic))+
  geom_bar(stat = "identity",  position = "dodge") +
  labs(title = "Completers VS non-completers repayment rate",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5))

# ggplot(completer, aes(x = year, y = median, color = characteristic))+
#   geom_point(alpha = 0.7) +
#   geom_path(size = 1) +
#   facet_grid(.~period)
# 
# ggplot(completer, aes(x = year, y = median))+
#   geom_bar(aes(fill = characteristic),stat = "identity",  position = "dodge", alpha = 0.7) +
#   geom_path(aes(color = characteristic), size = 1)+
#   facet_wrap(~period)
```

7. dependent
```{r}
dependent <- rt_median[sapply(rt_median$characteristic, function(x) grepl("dependent", x)),]
ggplot(dependent, aes(x = factor(year), y = median, fill = characteristic))+
  geom_bar(stat = "identity",  position = "dodge") +
  labs(title = "Dependent VS independent students repayment rate",
       x = "Year",
       y = "Repayment rate")+
  theme(plot.title = element_text(hjust = 0.5))

# ggplot(dependent, aes(x = year, y = median, color = characteristic))+
#   geom_point(alpha = 0.7) +
#   geom_path(size = 1) +
#   facet_grid(.~period)
# 
# ggplot(dependent, aes(x = year, y = median))+
#   geom_bar(aes(fill = characteristic),stat = "identity",  position = "dodge", alpha = 0.7) +
#   geom_path(aes(color = characteristic), size = 1)+
#   facet_wrap(~period)
```

8. pell_grant
```{r}
# pell <- rt_median[sapply(rt_median$characteristic, function(x) grepl("pell", x)),]
# ggplot(pell, aes(x = factor(year), y = median, fill = characteristic))+
#   geom_bar(stat = "identity",  position = "dodge")
# 
# ggplot(pell, aes(x = year, y = median, color = characteristic))+
#   geom_point(alpha = 0.7) +
#   geom_path(size = 1) +
#   facet_grid(.~period)
# 
# ggplot(pell, aes(x = year, y = median))+
#   geom_bar(aes(fill = characteristic),stat = "identity",  position = "dodge", alpha = 0.7) +
#   geom_path(aes(color = characteristic), size = 1)+
#   facet_wrap(~period)
```



# rp_n
```{r}
rp_n$period[rp_n$name == "rpy_1yr_n"] <- "1_year"
rp_n$period[rp_n$name == "rpy_3yr_n"] <- "3_year"
rp_n$period[rp_n$name == "rpy_5yr_n"] <- "5_year"
rp_n$period[rp_n$name == "rpy_7yr_n"] <- "7_year"
```

```{r}
n_median <- rp_n %>% 
  group_by(year, period) %>% 
  summarise(median = median(value, na.rm = T))

n_median
```

```{r}
ggplot(n_median, aes(x = year, y = median, color = period)) +
  geom_path(size = 1)+
  labs(title = "Number of students in different periods of year-repayment cohort",hjust = 0.5,
       x = "Year",
       y = "Number of students")
  
```



